Supporting Information : Impact of asymmetric tail-dependence in extreme climatic events on extinction risk in population ecology

### 2019-03-19 SuppMat.Rmd
plot changed notation sigma for standard deviation

lines(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_right_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025right,x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
legend("bottomright", c("Ricker",paste0("K = ",K),paste0("sd =",scl)), horiz=F, bty='n',cex=1.8)
#legend("bottomright", c("noise : LTdep.","noise : RTdep."), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=F, bty='n',cex=1.5)
par(op)
dev.off()
```

@@

lines(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_right_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025right,x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
legend("bottomright", c("Hassell",paste0("a = ",a," ,b = ",b),paste0("sd =",scl)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()
```

@@

lines(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_right_d0,col="blue",type="b",pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025right,x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
legend("bottomright", c("Maynard Smith",paste0("a = ",a," ,b = ",b),paste0("sd =",scl)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()
```

@@

lines(pennycuick_extrisk_d0$r,pennycuick_extrisk_d0$risk_right_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=pennycuick_extrisk_d0$r,y0=pennycuick_extrisk_d0$CI0.025right,x1=pennycuick_extrisk_d0$r,y1=pennycuick_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
legend("bottomright", c("Pennycuick",paste0("a = ",a," ,b = ",b),paste0("sd =",scl)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()
```

@@

lines(verhulst_extrisk_d0$r,verhulst_extrisk_d0$risk_right_d0,col="blue",type="b",pch=1)
arrows(x0=verhulst_extrisk_d0$r,y0=verhulst_extrisk_d0$CI0.025right,
       x1=verhulst_extrisk_d0$r,y1=verhulst_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
legend("bottomright", c("Verhulst",paste0("K =1, sd =",scl)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()
```

@@

lines(abrewer_extrisk_d0$r,abrewer_extrisk_d0$risk_right_d0,col="blue",type="b",pch=1)
arrows(x0=abrewer_extrisk_d0$r,y0=abrewer_extrisk_d0$CI0.025right,
       x1=abrewer_extrisk_d0$r,y1=abrewer_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
legend("bottomright", c("Austin-Brewer",paste0("s = ",s," , K = ",K),paste0(" sd =",scl)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()
```

@@

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
legend(x=0.7,y=1.05, c("noise : LTdep.","noise : RTdep."), lty=c(1,1), pch=c(1,1), 
       col=c('red', 'blue'), horiz=F, bty='o', cex=1.5, adj=0)
mtext(paste("Ricker model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(paste("(K = 50, sd = 1)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
getplot(x=x,rlist = rlist)

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Hassell model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(paste("(a = 0.5, b = 100, sd = 1)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
x<-res_hassell_local
rlist<-hassell_extrisk_d0$r
getplot(x=x,rlist = rlist)

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Maynard Smith model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(paste("(a = 0.5, b = 4, sd = 0.8)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
x<-res_msmith_local
rlist<-msmith_extrisk_d0$r
getplot(x=x,rlist = rlist)

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Pennycuick model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(paste("(a = 0.1, b = 0.1, sd = 1)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
x<-res_pennycuick_local
rlist<-pennycuick_extrisk_d0$r
getplot(x=x,rlist = rlist)

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Verhulst model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(paste("(K = 1, sd = 0.6)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
x<-res_verhulst_local
rlist<-verhulst_extrisk_d0$r
getplot(x=x,rlist = rlist)

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Austin-Brewer model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(paste("(s = 0.2, K = 50, sd = 0.6)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
x<-res_abrewer_local
rlist<-abrewer_extrisk_d0$r
getplot(x=x,rlist = rlist)

@@

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
legend(x=0.7,y=1.05, c("noise : LTdep.","noise : RTdep."), lty=c(1,1), pch=c(1,1), 
       col=c('red', 'blue'), horiz=F, bty='o', cex=1.5, adj=0)
mtext(paste("Ricker model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(paste("(K = 50, sd = 1)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
getplot(x=x,rlist = rlist)

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Hassell model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(paste("(a = 0.5, b = 100, sd = 1)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
x<-res_hassell_global
rlist<-hassell_extrisk_d0$r
getplot(x=x,rlist = rlist)

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Maynard Smith model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(paste("(a = 0.5, b = 4, sd = 0.8)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
x<-res_msmith_global
rlist<-msmith_extrisk_d0$r
getplot(x=x,rlist = rlist)

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Pennycuick model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(paste("(a = 0.1, b = 0.1, sd = 1)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
x<-res_pennycuick_global
rlist<-pennycuick_extrisk_d0$r
getplot(x=x,rlist = rlist)

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Verhulst model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(paste("(K = 1, sd = 0.6)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
x<-res_verhulst_global
rlist<-verhulst_extrisk_d0$r
getplot(x=x,rlist = rlist)

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Austin-Brewer model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(paste("(s = 0.2, K = 50, sd = 0.6)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
x<-res_abrewer_global
rlist<-abrewer_extrisk_d0$r
getplot(x=x,rlist = rlist)

@@

dt1 <- tibble("Models $(P_{t+1}^{i} = \\lambda_t^{i} P_t^{i})$"= c("Ricker",
           "Hassell",
           "Maynard Smith",
           "Pennycuick",
           "Verhulst",
           "Austin-Brewer")
)

@@

dt3<-tibble("\\hspace{-0.1 cm} Parameters used" = c("K = 50, sd = 1",
                            "a = 0.5, b = 100, sd = 1",
                            "a = 0.5, b = 4, sd = 0.8",
                           "a = 0.1, b= 0.1, sd = 1",
                           "K = 1, sd = 0.6",
                           "s = 0.2, K = 50, sd = 0.6"
))

@@

<!--Supp. FIG : Ricker model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_local_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Ricker dynamics with local dispersal; 
numsims=10000, sd=1. \label{fig_ricker_risk_local_disp_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Ricker model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_global_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Ricker dynamics with global dispersal; 
numsims=10000, sd=1. \label{fig_ricker_risk_global_disp_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Hassell model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/hassell_scl_1/hassell_ext_risk_local_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Hassell dynamics with local dispersal; 
numsims=10000, sd=1. \label{fig_hassell_risk_local_disp_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Hassell model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/hassell_scl_1/hassell_ext_risk_global_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Hassell dynamics with global dispersal; 
numsims=10000, sd=1. \label{fig_hassell_risk_global_disp_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Maynard smith model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/msmith_scl_0.8/msmith_ext_risk_local_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Maynard Smith dynamics with local dispersal; 
numsims=10000, sd=0.8. \label{fig_msmith_risk_local_disp_scl_0.8}}
\end{center}
\end{figure}

<!--Supp. FIG : Maynard smith model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/msmith_scl_0.8/msmith_ext_risk_global_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Maynard Smith dynamics with global dispersal; 
numsims=10000, sd=0.8. \label{fig_msmith_risk_global_disp_scl_0.8}}
\end{center}
\end{figure}

<!--Supp. FIG : Pennycuick model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/pennycuick_scl_1/pennycuick_ext_risk_local_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Pennycuick dynamics with local dispersal; 
numsims=10000, sd=1. \label{fig_risk_local_disp_pennycuick_r_vary_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Pennycuick model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/pennycuick_scl_1/pennycuick_ext_risk_global_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Pennycuick dynamics with global dispersal; 
numsims=10000, sd=1. \label{fig_risk_global_disp_pennycuick_r_vary_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Verhulst model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/verhulst_scl_0.6/verhulst_ext_risk_local_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Verhulst dynamics with local dispersal; 
numsims=10000, sd=0.6. \label{fig_risk_local_disp_verhulst_r_vary_scl_0.6}}
\end{center}
\end{figure}

<!--Supp. FIG : Verhulst model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/verhulst_scl_0.6/verhulst_ext_risk_global_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Verhulst dynamics with global dispersal; 
numsims=10000, sd=0.6. \label{fig_risk_global_disp_verhulst_r_vary_scl_0.6}}
\end{center}
\end{figure}

<!--Supp. FIG : Austin brewer model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/austinbrewer_scl_0.6/abrewer_ext_risk_local_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Austin-Brewer dynamics with local dispersal; 
numsims=10000, sd=0.6. \label{fig_risk_local_disp_abrewer_r_vary_scl_0.6}}
\end{center}
\end{figure}

>>>>

lines(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_right_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025right,x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
legend("topleft", legend=c("Ricker"), horiz=F, bty='n',cex=1.8)  
mtext(paste0("K = ",K),side = 3, line=-16, adj=0.95, cex=1.8, col="black")
legend("bottomright",legend=bquote(sigma==.(scl)), horiz=F,bty='n',cex=1.8)
#legend("bottomright", legend=c("Ricker",paste0("K = ",K)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()
```

@@

lines(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_right_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025right,x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
legend("topleft", legend=c("Hassell"), horiz=F, bty='n',cex=1.8)  
mtext(paste0("a = ",a,", b = ",b),side = 3, line=-16, adj=0.9, cex=1.8, col="black")
legend("bottomright",legend=bquote(sigma==.(scl)), horiz=F,bty='n',cex=1.8)
#legend("bottomright", c("Hassell",paste0("a = ",a," ,b = ",b),paste0("sd =",scl)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()
```

@@

lines(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_right_d0,col="blue",type="b",pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025right,x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
legend("topleft", legend=c("Maynard Smith"), horiz=F, bty='n',cex=1.8)  
mtext(paste0("a = ",a,", b = ",b),side = 3, line=-16, adj=0.9, cex=1.8, col="black")
legend("bottomright",legend=bquote(sigma==.(scl)), horiz=F,bty='n',cex=1.8)
par(op)
dev.off()
```

@@

lines(pennycuick_extrisk_d0$r,pennycuick_extrisk_d0$risk_right_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=pennycuick_extrisk_d0$r,y0=pennycuick_extrisk_d0$CI0.025right,x1=pennycuick_extrisk_d0$r,y1=pennycuick_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
legend("topleft", legend=c("Pennycuick"), horiz=F, bty='n',cex=1.8)  
mtext(paste0("a = ",a,", b = ",b),side = 3, line=-16, adj=0.9, cex=1.8, col="black")
legend("bottomright",legend=bquote(sigma==.(scl)), horiz=F,bty='n',cex=1.8)
#legend("bottomright", c("Pennycuick",paste0("a = ",a," ,b = ",b),paste0("sd =",scl)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()
```

@@

lines(verhulst_extrisk_d0$r,verhulst_extrisk_d0$risk_right_d0,col="blue",type="b",pch=1)
arrows(x0=verhulst_extrisk_d0$r,y0=verhulst_extrisk_d0$CI0.025right,
       x1=verhulst_extrisk_d0$r,y1=verhulst_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
legend("topleft", legend=c("Verhulst"), horiz=F, bty='n',cex=1.8)  
mtext(paste0("K = ",K),side = 3, line=-16, adj=0.9, cex=1.8, col="black")
legend("bottomright",legend=bquote(sigma==.(scl)), horiz=F,bty='n',cex=1.8)
#legend("bottomright", c("Verhulst",paste0("K =1, sd =",scl)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()
```

@@

lines(abrewer_extrisk_d0$r,abrewer_extrisk_d0$risk_right_d0,col="blue",type="b",pch=1)
arrows(x0=abrewer_extrisk_d0$r,y0=abrewer_extrisk_d0$CI0.025right,
       x1=abrewer_extrisk_d0$r,y1=abrewer_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
legend("topleft", legend=c("Austin-Brewer"), horiz=F, bty='n',cex=1.8)  
mtext(paste0("s = ",s,", K = ",K),side = 3, line=-16, adj=0.9, cex=1.8, col="black")
legend("bottomright",legend=bquote(sigma==.(scl)), horiz=F,bty='n',cex=1.8)
#legend("bottomright", c("Austin-Brewer",paste0("s = ",s," , K = ",K),paste0(" sd =",scl)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()
```

@@

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
legend(x=0.7,y=1.05, c("noise : LTdep.","noise : RTdep."), lty=c(1,1), pch=c(1,1), 
       col=c('red', 'blue'), horiz=F, bty='o', cex=1.5, adj=0)
mtext(paste("Ricker model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
#mtext(paste("(K = 50, sd = 1)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
mtext(expression( paste("( K = 50, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
getplot(x=x,rlist = rlist)

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Hassell model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.5, b = 100, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_hassell_local
rlist<-hassell_extrisk_d0$r
getplot(x=x,rlist = rlist)

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Maynard Smith model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.5, b = 4, ", sigma,"=0.8 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_msmith_local
rlist<-msmith_extrisk_d0$r
getplot(x=x,rlist = rlist)

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Pennycuick model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.1, b = 0.1, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_pennycuick_local
rlist<-pennycuick_extrisk_d0$r
getplot(x=x,rlist = rlist)

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Verhulst model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( K = 1, ", sigma,"=0.6 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_verhulst_local
rlist<-verhulst_extrisk_d0$r
getplot(x=x,rlist = rlist)

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Austin-Brewer model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( s = 0.2, K = 50, ", sigma,"=0.6 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_abrewer_local
rlist<-abrewer_extrisk_d0$r
getplot(x=x,rlist = rlist)

@@

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
legend(x=0.7,y=1.05, c("noise : LTdep.","noise : RTdep."), lty=c(1,1), pch=c(1,1), 
       col=c('red', 'blue'), horiz=F, bty='o', cex=1.5, adj=0)
mtext(paste("Ricker model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( K = 50, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
getplot(x=x,rlist = rlist)

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Hassell model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.5, b = 100, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_hassell_global
rlist<-hassell_extrisk_d0$r
getplot(x=x,rlist = rlist)

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Maynard Smith model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.5, b = 4, ", sigma,"=0.8 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_msmith_global
rlist<-msmith_extrisk_d0$r
getplot(x=x,rlist = rlist)

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Pennycuick model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.1, b = 0.1, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_pennycuick_global
rlist<-pennycuick_extrisk_d0$r
getplot(x=x,rlist = rlist)

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Verhulst model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( K = 1, ", sigma,"=0.6 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_verhulst_global
rlist<-verhulst_extrisk_d0$r
getplot(x=x,rlist = rlist)

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Austin-Brewer model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( s = 0.2, K = 50, ", sigma,"=0.6 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_abrewer_global
rlist<-abrewer_extrisk_d0$r
getplot(x=x,rlist = rlist)

@@

dt1 <- tibble("Models"= c("Ricker",
           "Hassell",
           "Maynard Smith",
           "Pennycuick",
           "Verhulst",
           "Austin-Brewer")
)

@@

dt3<-tibble("\\hspace{-0.1 cm} Parameters used" = c("K = 50, $\\sigma$ = 1",
                            "a = 0.5, b = 100, $\\sigma$ = 1",
                            "a = 0.5, b = 4, $\\sigma$ = 0.8",
                           "a = 0.1, b= 0.1, $\\sigma$ = 1",
                           "K = 1, $\\sigma$ = 0.6",
                           "s = 0.2, K = 50, $\\sigma$ = 0.6"
))

@@

<!--Supp. FIG : Ricker model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_local_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Ricker dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_ricker_risk_local_disp_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Ricker model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_global_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Ricker dynamics with global dispersal; 
numsims=10000, $\sigma$=1. \label{fig_ricker_risk_global_disp_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Hassell model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/hassell_scl_1/hassell_ext_risk_local_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Hassell dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_hassell_risk_local_disp_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Hassell model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/hassell_scl_1/hassell_ext_risk_global_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Hassell dynamics with global dispersal; 
numsims=10000, $\sigma$=1. \label{fig_hassell_risk_global_disp_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Maynard smith model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/msmith_scl_0.8/msmith_ext_risk_local_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Maynard Smith dynamics with local dispersal; 
numsims=10000, $\sigma$=0.8. \label{fig_msmith_risk_local_disp_scl_0.8}}
\end{center}
\end{figure}

<!--Supp. FIG : Maynard smith model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/msmith_scl_0.8/msmith_ext_risk_global_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Maynard Smith dynamics with global dispersal; 
numsims=10000, $\sigma$=0.8. \label{fig_msmith_risk_global_disp_scl_0.8}}
\end{center}
\end{figure}

<!--Supp. FIG : Pennycuick model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/pennycuick_scl_1/pennycuick_ext_risk_local_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Pennycuick dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_risk_local_disp_pennycuick_r_vary_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Pennycuick model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/pennycuick_scl_1/pennycuick_ext_risk_global_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Pennycuick dynamics with global dispersal; 
numsims=10000, $\sigma$=1. \label{fig_risk_global_disp_pennycuick_r_vary_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Verhulst model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/verhulst_scl_0.6/verhulst_ext_risk_local_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Verhulst dynamics with local dispersal; 
numsims=10000, $\sigma$=0.6. \label{fig_risk_local_disp_verhulst_r_vary_scl_0.6}}
\end{center}
\end{figure}

<!--Supp. FIG : Verhulst model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/verhulst_scl_0.6/verhulst_ext_risk_global_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Verhulst dynamics with global dispersal; 
numsims=10000, $\sigma$=0.6. \label{fig_risk_global_disp_verhulst_r_vary_scl_0.6}}
\end{center}
\end{figure}

<!--Supp. FIG : Austin brewer model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/austinbrewer_scl_0.6/abrewer_ext_risk_local_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Austin-Brewer dynamics with local dispersal; 
numsims=10000, $\sigma$=0.6. \label{fig_risk_local_disp_abrewer_r_vary_scl_0.6}}
\end{center}
\end{figure}
